A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-21 text/properties.tex
Remove a comment.
FInish revising Seciton 1.
Substitutions in type environment.
Finish revising Section 4.

\section{Properties of \LMD}

@@

We let $\mathcal{J}$ stand for judgments $K \iskind @A$, $\tau::K@A$,
$M:\tau@A$, $K \E J @ A$, $\tau \E \sigma @ A$, and
$M \E N : \tau @ A$.  Substitutions $\mathcal{J}[z \mapsto M]$ and
$\mathcal{J}[\alpha \mapsto A]$ are defined in a straightforward
manner.  Using these notations, the two substitution lemmas are stated as follows:
\AI{Did we define $\Delta [x \mapsto N]$?}

@@

\begin{proof}
	First, there are three cases for $M \longrightarrow M'$.
	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
	For each case, we can use straightforward induction on derivations. \AI{何の derivation?}
	Difficult cases are \TApp, \TTBL, and \TIns.
	We need Inversion Lemmas for them.
\end{proof}

@@

Strong Normalization is also an important property, which guarantees that
no typed term has an infinite reduction sequence.
We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{Tsukada} \AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.

@@

\AI{Don't we prove $\longrightarrow_s$ is a subrelation of $\longrightarrow$?}

>>>>

\section{Properties of \LMD \label{sec:properties}}

@@

We let $\mathcal{J}$ stand for judgments $K \iskind @A$, $\tau::K@A$,
$M:\tau@A$, $K \E J @ A$, $\tau \E \sigma @ A$, and
$M \E N : \tau @ A$.  Substitutions $\mathcal{J}[z \mapsto M]$ and
$\mathcal{J}[\alpha \mapsto A]$ are defined in a straightforward
manner.  Using these notations, the two substitution lemmas are stated as follows:

@@

\begin{proof}
	First, there are three cases for $M \longrightarrow M'$.
	They are $M \longrightarrow_\beta M'$, $M \longrightarrow_\Lambda M'$, and $M \longrightarrow_\blacklozenge M'$.
	For each case, we can use straightforward induction on typing derivations.
	Difficult cases are \TApp, \TTBL, and \TIns.
	We need Inversion Lemmas for them.
\end{proof}

@@

Strong Normalization is also an important property, which guarantees that
no typed term has an infinite reduction sequence.
We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{harper1993framework}.
\AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.
\red{とりあえずA Framework for Defining Logicsを引用しました。}

@@
